---
title: "Module 4 Assignment"
author: "Kevin Gardner"
date: '2022-10-02'
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

# ------------------------------------------------
# Following is the link to my GitHub account:
# https://github.com/Kgardner22/64018_kgardner
# ------------------------------------------------

LP Problem: The Weigelt Corporation

If lpSolveAPI is not already installed, remove the "*" preceeding lines 26-30 and run the block:

*Install lpSolveAPI

*```{r}
*install.packages("lpSolveAPI")
*```

load the needed library
```{r}
library(lpSolveAPI)
```

We will setup the Weigelt Corporation problem. Note, we have nine (9) decision variables and twelve (12) constraints. We also have nine (9) non-negativity constraints.

We will read the lp formulation using an lp file. 

```{r}
x <- read.lp("Weigelt.lp") # create an lp object x
x                          # display x
```

Solve the lp model

```{r}
solve(x)
get.objective(x)        # get objective value
get.variables(x)        # get values of decision variables
get.constraints(x)      # get constraint RHS values
```




